Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-20 article.tex
typo

Overall, the work on simulating molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
to encapsulate all the relevant information of the system, and can simulate efficiently and without approximations.

@@

The wavefunction of a quantum system is a mathematical construct describing the state, it provides probabilities for results of particular measurements
 made on the state. In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed
  atomic nuclei. And so a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with
  their respective energies. The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer
  approximation. It is a very useful assumption that simplifies electronic structure calculations appreciably.

One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
  interest in the molecule. This is of great interest in for example the development of pharmaceuticals where companies have an extremely laborious
  testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
  and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.

>>>>

Overall, the work on simulating molecular energies with classical methods is a trade off between precision and cost. Quantum simulation is able
to encapsulate all the relevant information of the system, and can simulate efficiently and with high accuracy.

@@

The wavefunction of a quantum system is a mathematical construct describing the state; it provides probabilities for results of particular measurements
 made on the state. In quantum chemistry the electronic structure of a molecule is described by the movement of the electrons of a collection of fixed
  atomic nuclei. And thus a comprehensive description of the electronic structure encompasses the wavefunctions of all of these electrons, along with
  their respective energies. The idea that the motions of the electrons and nuclei may be considered separately is known as the Born-Oppenheimer
  approximation. It is a very useful assumption that simplifies electronic structure calculations appreciably.

One of the reasons that developing new approaches to tackling electronic structure calculations are of importance is that they are extremely
computationally expensive. Indeed one of the original motivations for the field of quantum computing was the desire to simulate quantum systems
 in nature by using quantum systems. A prominent driving factor in the interest in and development of quantum computing is the aim to create quantum
  hardware and software that will allow for efficient quantum simulations of chemical systems. A problem of tantamount importance in quantum chemistry
  is that of finding the lowest energy eigenvalue of molecular electronic structures. These energy eigenvalues define a great deal of properties of
  interest in the molecule. This is of great importance in for example the development of pharmaceuticals where companies have an extremely laborious
  testing and trials process, if a significant part of the initial testing process could be done in silico - this would represent significant savings
  and would better ensure that the pharmaceutical under development behaved as required prior to starting trials.
